% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{11in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Paul Batchelor}
\address{ 9 Winchester Rd\\   Newton, MA, 02458\\  (617) 775-1553 \\ www.pbat.ch}
\begin{resume}                        
 
\line(1, 0){250}                           
%\section{Objective}      Acquire an internship/job in the field of Music 
%Technology and/or sound design.
 
\section{Education}
                Center for Computer Research in Music and Acoustics \\
                Stanford University, Stanford, CA 2015-2017 \\
                MA in Music, Science, Technology \\
                \\
                Berklee College of Music, Boston, MA  2010-14\\
                Bachelor of Music in Electronic Production and Design, Summa Cum Laude\\
 
\section{Skills} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Languages
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] C, C++ (proficient), Csound, FAUST, Lua, Python (proficient), 
Perl (proficient), Bash/Shell, sed/AWK, Scheme (proficient)
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Audio 
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] DAW Plugin Development, Audio Digital Signal Processing, JUCE, MATLAB/Octave, Numpy/SciPy, Mixing, 
Studio Recording, Sound design, Pro Tools, Reaper, Renoise, PD
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Embedded Devices
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Arduino/AVR, STM32F series ARM boards, Raspberry Pi
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Graphics
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] OpenGL, Blender, Inkscape, GIMP, LaTeX
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Software Engineering
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Git/Github, Trello, Jira, Agile, GDB, Valgrind, 
    Prior experience in: Mercurial SVN, Puppet, Chef, Vagrant, Docker
\end{itemize} 


\section{Experience}      

\begin{tabular}{p{3in} r} 
QuBit Electronics &  Summer 2016
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Research and Development in floating point ARM devices. Also helped 
integrate modern software practices with the team through tools like Git and
Trello.
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Google ATAP & Winter 2016
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Part of the project SOLI alpha developers program. Created proof-of-concept
music software that used microgestures to control realtime audio synthesis 
parameters via the Soli. 
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Safari Books Online &  Summer 2014 - Spring 2015
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Systems Administrator intern. Learned about systems engineering 
practices and gained experience with team and project management. 
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
QuBit Electronix&  Summer 2014
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Sound designer and primary Linux developer for Nebulae Module. 
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
% is 3 inches wide
BT, Leap Motion, Boulanger Labs&  Fall 2013
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Instrument design for Leap Motion app Muse.
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
% is 3 inches wide
Boulanger Labs&  Fall/Spring 2012-13
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Sound designer, developer, and product tester for iPad App csSpectral.
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Berklee College of Music&  Fall 2013
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Teaching assistant for courses EP-337 (Programming, Sound Design, and
Composition for Csound) and EP-353 (Programming Audio Applications in C, C++, and 
Objective C)
\end{itemize} 

\begin{tabular}{p{3in} r} % setup 2 columns, first
Audivation&   Fall/Spring 2012-13
\end{tabular}	
\begin{itemize} % \item[] prevents a bullet from appearing
\item[] Product testing and code maintenance for Csound4Live plugins. 
\end{itemize} 

\begin{tabular}{p{3in} r} % one column is 3 inches wide
Longy School of Music&  2008-10
\end{tabular}
\begin{itemize}					        
\item[] Principle Bass for the Longy Youth Chamber Orchestra.
\end{itemize}
\end{resume} 
\end{document}
