% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Paul Batchelor}

\address{ 9 Winchester Rd\\   Newton, Ma, 02458\\   (617) 775-1553 }
                           
                        
\begin{resume}                        
 
\section{OBJECTIVE}       A full-time job in a music-technology related field.
 
\section{EDUCATION}      Berklee College of Music, Boston, MA \\
                Bachelor of Music, expected May 2013\\
 
                \begin{ncolumn}{2}
                {\bf Major Subjects}   &  {\bf Minor Subjects} \\
                Digital Production and Design &  Avant Garde Composition \\
                Advanced Sound Design &  Intro to Film Scoring \\
                Control Systems        &  Audio Programming\\
                Application Design &  Microcontrollers \\
                Audio Engineering &  Csound \\
                Mix Techniques &  Digital Signal Processing \\
 
		\end{ncolumn}
 
\section{SKILLS} 
\normalsize{\section{Sound/Instrument Design}}
                 \begin{itemize}
                 \item Optimized and designed several real-time instruments to be
played on the Raspberry Pi for Csound Journal.
			  \item Expert knowledge in of synthesis and DSP techniques using Csound.
                 \end{itemize}
\normalsize{\section{Linux Systems}} 
                 \begin{itemize}
                  \item  Working knowledge of 
Linux architecture. Intermediate knowledge of grep, perl, bash, python. Specialty
in Pro-Audio Linux Systems.
			   \item Developed the official Raspberry Pi Demo at Berklee College
of Music.
                  \end{itemize}
\normalsize{\section{Musicianship}} 
                 \begin{itemize}
                  \item Accepted into Berklee on upright bass. Capable of playing
a wide range of styles. Experience in professional and semi-professional orchestras,
jazz combos, and rock bands. Proficient at reading music and teaching.
                  \end{itemize}

\normalsize{\section{Leadership}}
	           \begin{itemize} \itemsep -2pt % reduce space between items
                   \item Founder of Berklee's Linux Club
                   \item Leading Raspberry Pi expert at Berklee.
                  \item Principal Bass of district orchestra for 2 years. Principal
Bassist of Longy Youth Symphony Orchestra from 2008-2010
                   \item Executive band coordinator for Newton's FUSN youth coffeehouse, 
2008-2010.
                   \end{itemize}
\normalsize{\section{Communication}} 
                  \begin{itemize} \itemsep -2pt
                  \item Frequent guest speaker for Richard Boulanger's Csound 
class.
                  \item  Presented lecture on Vim techniques in Berklee's computer
science club.
                  \item  MC for FUSN Coffeehouse, 2008
                  \end{itemize} 
 
\section{EXPERIENCE}      
                  \begin{tabular}{p{3in} r} % setup 2 columns, first
					    % is 3 inches wide
                  Boulanger Labs &  Fall/Spring 2012-13
                  \end{tabular}	
                   \begin{itemize} % \item[] prevents a bullet from appearing
                    \item[] Developer for csSpectral app for the iPad.
		   \end{itemize} 
		 \begin{tabular}{p{3in} r}
                  LinuxCon Boston &  Summer 2010
                 \end{tabular}	
		  \begin{itemize}
                   \item[] Brought on as volunteer to assist organizer.
                  \end{itemize}
                 \begin{tabular}{p{3in} r} % one column is 3 inches wide
                  Boston Artists Ensemble &  2009-2013
                 \end{tabular}
                  \begin{itemize}					        
                   \item[] Acoustic/Technical Assistance.
                  \end{itemize}
\section{HONORS} Dean's List \\
                 Recipient of the 2010 Lasker Award at Newton North High School\\
			  Honorable Mention in the 2011 Berklee Sound Collage Contest
 
\section{ACTIVITIES}
			 Linux Club organizer, Computer Science Club\\
			 Bassist/Vocals in Band "The Ukulele Brothers"
\section{HOBBIES}         Ring Maille, Composition, Programming
 
\end{resume} 
\end{document}









